Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal

### 2010-01-23 trunk/doc/msc-proposal/msc-snmp.tex
proposal: added SNMP architecture image

\section{SNMP Concepts}
* SNMPv1 and SNMPv2 have two kinds of entities: managers and agents.

* SNMPv3 makes a big change to the basic concepts and abandons the notion of managers and agents, both are now called SNMP entities.

\section{The Structure of Management Information (SMI)}

\section{Management Information Base}

\section{Protocol Architecture}

\subsection{SNMPv3 Engine}

\subsection{The SNMPv3 Applications}

>>>>

\section{Protocol Architecture}
The SNMP protocol consists of four basic components: an entity which provides remote access to management instrumentation (typically called as an agent); an entity running management applications (typically called a manager); a management protocol to convey management information between the entities; and management information.

According to the SNMP architecture \cite{rfc3411}, an SNMP entity consists of an SNMP engine and one or more associated applications.

\begin{figure}	
\begin{center}
    \includegraphics[scale = 0.6]{img/snmp-arch.pdf}
    \caption{Structure of an SNMP entity}   
	\label{fig:snmparch}
\end{center}
\end{figure}
